Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/evaluation.tex
Temp Save

\begin{figure}[t!]
    \centering
    % \begin{subfigure}[b]{0.05\textwidth}
    %         \includegraphics[width=\textwidth]{resources/Fig_Variance/image_0}
    % \end{subfigure}
    % \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_1}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_2}
    \end{subfigure}
    \hfill
    % \begin{subfigure}[b]{0.07\textwidth}
    %         \includegraphics[height=4.8cm]{resources/Fig_Variance/image_3}
    % \end{subfigure}
    % \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_4}
    \end{subfigure}
  	\hfill
    % \begin{subfigure}[b]{0.05\textwidth}
    %         \includegraphics[width=\textwidth]{resources/Fig_Variance/image_5}
    % \end{subfigure}
    % \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_6}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.125\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/variances}
    \end{subfigure}
    \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
    \label{fig:variance}
\end{figure}

@@

\begin{figure*}[t!]
    \newcommand{\ofh}{0.24\columnwidth}
    \centering
    \includegraphics[height=\ofh]{resources/Fixing/fix_3}
    \includegraphics[height=\ofh]{resources/Fixing/fix_5}
    \includegraphics[height=\ofh]{resources/Fixing/fix_6}
    \includegraphics[height=\ofh]{resources/Fixing/fix_7}
    \includegraphics[height=\ofh]{resources/Fixing/fix_8}
    \includegraphics[height=\ofh]{resources/Fixing/fix_9}
    \includegraphics[height=\ofh]{resources/Fixing/fix_10}
    \includegraphics[height=\ofh]{resources/Fixing/fix_12}
    \includegraphics[height=\ofh]{resources/Fixing/fix_13}
    \includegraphics[height=\ofh]{resources/Fixing/fix_14}
    \includegraphics[height=\ofh]{resources/Fixing/fix_15}
    \includegraphics[height=\ofh]{resources/Fixing/fix_17}
    \includegraphics[height=\ofh]{resources/Fixing/fix_18}
    \includegraphics[height=\ofh]{resources/Fixing/fix_19}
    \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}}
    \label{fig:outline_fitting}
\end{figure*}

>>>>

\begin{figure}[t!]
    \centering
    \newcommand{\vfh}{4cm}
    \includegraphics[height=\vfh]{resources/Fig_Variance/image_1}
    \includegraphics[height=\vfh]{resources/Fig_Variance/image_2}
    \includegraphics[height=\vfh]{resources/Fig_Variance/image_4}
    \includegraphics[height=\vfh]{resources/Fig_Variance/image_6}
    \includegraphics[height=\vfh]{resources/Fig_Variance/variances}
    \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
    \label{fig:variance}
\end{figure}

@@

\begin{figure*}[t!]
    \newcommand{\ofh}{0.24\columnwidth}
    \centering
    \includegraphics[height=\ofh]{resources/Fittings/1.eps}
    \includegraphics[height=\ofh]{resources/Fittings/3.eps}
    \includegraphics[height=\ofh]{resources/Fittings/4.eps}
    \includegraphics[height=\ofh]{resources/Fittings/6.eps}
    \includegraphics[height=\ofh]{resources/Fittings/7.eps}
    \includegraphics[height=\ofh]{resources/Fittings/8.eps}
    \includegraphics[height=\ofh]{resources/Fittings/13.eps}
    \includegraphics[height=\ofh]{resources/Fittings/15.eps}
    \includegraphics[height=\ofh]{resources/Fittings/17.eps}
    \includegraphics[height=\ofh]{resources/Fittings/19.eps}
    \includegraphics[height=\ofh]{resources/Fittings/21.eps}
    \includegraphics[height=\ofh]{resources/Fittings/23.eps}
    \includegraphics[height=\ofh]{resources/Fittings/25.eps}
    \includegraphics[height=\ofh]{resources/Fittings/27.eps}
    \includegraphics[height=\ofh]{resources/Fittings/29.eps}
    \includegraphics[height=\ofh]{resources/Fittings/31.eps}
    \includegraphics[height=\ofh]{resources/Fittings/33.eps}
    \includegraphics[height=\ofh]{resources/Fittings/35.eps}
    \includegraphics[height=\ofh]{resources/Fittings/36.eps}
    \includegraphics[height=\ofh]{resources/Fittings/37.eps}
    \includegraphics[height=\ofh]{resources/Fittings/38.eps}
    \includegraphics[height=\ofh]{resources/Fittings/39.eps}
    \caption{Demonstration of outline fitting of patch AAM}
    \label{fig:outline_fitting}
\end{figure*}
